A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-22 paper.tex
woops
5d

@@

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric, where $\fg$ is the complexified Lie algebra of the gauge group.

@@

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.

@@

Suppose $L$ is a complex vector space equipped with a K\"ahler structure and a complex half-density. Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR = L\times N$ (a 10-dimensional real vector space). By the results of Section \ref{sect:10dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density.

@@

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.

@@

@@

Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.

@@

We have $Q=\alpha\otimes w\in S\otimes W$ and denote by $\alpha\colon \U(1)\hookrightarrow G_R=\Spin(3, \RR)$ the subgroup under which $w$ has weight $1$. We consider the twisting homomorphism given by the composite
\[\phi\colon \MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]
As before, the $\MU(3)$-action on the theory factors through a $\U(3)$-action.

\begin{thm}
The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\RR^7$ is perturbatively equivalent to the generalized BF theory on $\CC^3\times \RR$ with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:7dminimaltwist}
\end{thm}
\begin{proof}
The minimal supercharge $Q=\alpha\otimes w$ may be obtained by dimensional reduction of the holomorphic supercharge in the 8-dimensional supersymmetry algebra. Therefore, the minimal twist of 7d $\cN=1$ super Yang--Mills on $\CC^3\times \RR$ is obtained by dimensional reduction from the holomorphic twist of 8d $\cN=1$ super Yang--Mills on $\CC^4$. The claim then follows from Theorem \ref{thm:8dholomorphictwist} and Corollary \ref{cor:BFholomorphicreduction}.
\end{proof}

@@

Next we study the topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L\times \RR$. Under $\SU(L)\subset \Spin(V_\RR)$ the spin representation decomposes as
\[S\cong \wedge^\bullet L.\]
In particular, it contains two trivial summands: $\CC\alpha$ in the lowest degree and $\CC\beta$ in the top degree.

Consider a family of square-zero supercharges
\begin{equation}
Q_t = (\alpha + t\beta)\otimes w
\label{eq:7dHodgefamily}
\end{equation}
for some nonzero $w\in W$. We have $(\alpha + t\beta, \alpha + t\beta)=t$, so at $t=0$ we have a minimal supercharge and at $t\neq 0$ we have a topological supercharge.

\begin{thm}
The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:7dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions. The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$. The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
\end{proof}

@@

%Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing. 
%The general theory with $\mc N = (1,0)$ supersymmetry consists of pure super Yang-Mills with Lie algebra $\fg$ coupled to $(1,0)$ matter valued in a symplectic vector space $U$, as in Section \ref{sect:mattermultipletSUSY}. 
%In physics terminology, the matter here is referred to as the $6d$ $\mc N = (1,0)$ hypermultiplet.
%
%The $R$-symmetry group is $G_R = \SU(2)$. \brian{Or do we want it's noncompact form ${\rm Sp}(W_+) = {\rm Sp}(2, \CC)$. }

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills Theory}

The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $U$ a complex symplectic $\fg$-representation. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.

@@

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

@@

We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]

Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$. Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.

\begin{thm}
The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$. Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
\end{thm}
\begin{proof}
The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.

To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$. In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}. The claim then follows from a direct comparison.
\end{proof}

@@

Next we study the rank $(1, 1)$ topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$. Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
\[
S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
\]
Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in \Sigma.
\label{eq:6dHodgefamily}
\end{equation}
At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.

\begin{thm}
The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:6dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}. So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills. Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
\end{proof}

@@

We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.

\begin{thm}
The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
\label{thm:6drank22}
\end{thm}
\begin{proof}
Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.

Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e. $s_+^\pm, s_-^\pm$ are all nonzero. The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.

$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$. But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.

So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$. The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
\end{proof}

\section{Dimension 5}
The 5-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 4-dimensional spinor representation of $\Spin(5) \iso \Sp(4)$, and where $W$ is a $2k$-dimensional symplectic vector space.  The maximal supersymmetric gauge theory has $\mc N=2$.  However, there are $\mc N=1$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group.

\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang-Mills Theory with Matter}  \label{5d_1_section}
We begin by treating $\mc N=1$ Super Yang-Mills theory with gauge group $G$, with a matter (half) hypermultiplet valued in a symplectic representation $U$.  This is the theory obtained from 6d $\mc N=(1,0)$ super Yang-Mills theory with matter, after dimensional reduction to 5 dimensions.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=1$ super Yang-Mills by restricting the 6d fields from Section \ref{6d_10_section} to representations of the group $\mr O(5)$.  In addition to the ghost $c$, the fields we obtain are
\begin{itemize}
 \item $\gg$-valued bosons: a gauge field $A \in \Omega^1(\RR^5; \gg)$, and a scalar $\phi' \in \Omega^0(\RR^5; \gg)$.
 \item $U$-valued bosons: a (symplectic) scalar field $\phi \in \Omega^0(\RR^5; W \otimes U)$.
 \item $\gg$-valued fermions: a spinor $\lambda \in \Omega^0(\RR^5; S \otimes W \otimes \gg)$.
 \item $U$-valued fermions: a spinor $\psi \in \Omega^0(\RR^5; S \otimes U)$.
\end{itemize}

\vspace{-10pt}
\paragraph{Twisting data:}
There is a unique class of square-zero supercharges in the 5d $\mc N=1$ supersymmetry algebra.  Twists by such supercharges are minimal: they are invariant in three directions.  The stabilizer of a minimal supercharge is isomorphic to $\SU(2) \sub \Spin(5)$.

\begin{theorem} \label{thm: 5dholtwist}
The minimal twist of 5d $\mc N=1$ super Yang-Mills theory with gauge group $G$ and symplectic matter representation $U$, on the product of a Calabi-Yau surface $S$ and an oriented 1-manifold $L$ is equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $\mr{Map}(S \times L_{\mr{dR}}, U\ham G)$.
\end{theorem}

\begin{proof}
This follows from the calculation of the minimal twist in 6-dimensional $\mc N=(1,0)$ theory in Theorem \ref{thm:6dholomorphictwist} above, by applying Proposition \ref{CS_diml_red_prop} to dimensionally reduce along one of the non-invariant Calabi-Yau directions.
\end{proof}

>>>>

In the following sections we fix a complex Lie algebra $\fg$ equipped with a symmetric bilinear invariant nondegenerate pairing which should be thought of as the complexified Lie algebra of the gauge group.

@@

We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^{10}$ with the Euclidean metric.

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^9$ equipped with the Euclidean metric.

@@

Suppose $L$ is a complex vector space equipped with a Hermitian structure and a complex half-density. Suppose $N_\RR=\RR^{5-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR = L\times N$ (a 10-dimensional real vector space). By the results of Section \ref{sect:10dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density.

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^8$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(2, \RR)$ which acts with weight $1/2$ on $W$ and weight $-1/2$ on $W^*$.

@@

\subsubsection{Topological twist}
\label{sect:8dtopologicaltwist}

@@

We consider $\cN=1$ super Yang--Mills theory on $M=\RR^7$ with the Euclidean metric. It admits $R$-symmetry group $G_R=\Spin(3, \RR)$ with $W$ the two-dimensional spin representation.

@@

Suppose $L$ is a complex vector space equipped with a Hermitian structure. Suppose $N_\RR=\RR^{4-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR = L\times N$ (an 8-dimensional real vector space). We set $W^8=\det(L)^{-1/2}$ as a representation of $\MU(L)$. By the results of Section \ref{sect:8dholomorphictwist}, there is a canonical square-zero supercharge $Q\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\U(1)\times \Spin(N_\RR)$. We consider the grading $\alpha\colon \U(1)\rightarrow G_\RR$ given by the embedding into the first copy of $\U(1)$ and a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\xrightarrow{\det^{1/2}\times \id} G_R=\U(1)\times \Spin(N_\RR).\]

\begin{thm}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dBFreduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory. Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant. By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

We will now concentrate on the 7-dimensional case.

\begin{thm}
The minimal twist of 7d $\cN=1$ super Yang--Mills on $M=\CC^3\times \RR$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^3\times \RR_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:7dminimaltwist}
\end{thm}

@@

Next we study the topological twist. As in the case of the minimal twist, we will perform a computation applicable in lower dimensions as well.

Let $L$ be a complex vector space equipped with a Hermitian structure and a complex half-density. Suppose $N_\RR = \RR^{4-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR=L\times N$, a real 8-dimensional vector space equipped with a complex structure and a complex half-density. Using results of Section \ref{sect:8dtopologicaltwist} we obtain a family $Q_t$ of 8d square-zero supercharges.

The dimensional reduction of 8d $\cN=1$ super Yang--Mills on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ gives $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 16 supercharges. The $R$-symmetry group is $G_R=\Spin(N_\RR\oplus \RR^2)$ and we consider the grading given by the homomorphism $\alpha\colon\U(1)\hookrightarrow \Spin(2, \RR)\times \Spin(N_\RR)\subset G_R$ given by embedding into the first factor. We consider the twisting homomorphism given by $\Spin(N_\RR)\hookrightarrow \Spin(2, \RR)\times \Spin(N_\RR)\subset G_R$ given by embedding into the second factor.

\begin{thm}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q_t$ is perturbatively equivalent to the generalized Hodge theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, B\fg_\Hod)$. Moreover, the equivalence is $\SU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dHodgereduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:8dHodgetwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q_t$ is perturbatively equivalent to the holomorphic Hodge theory. Moreover, the equivalence is $\SU(L)\times \SU(N)$-equivariant. The claim then follows from Corollary \ref{cor:Hodgeholomorphicreduction}.
\end{proof}

Now let $L=\CC^3$ and $N_\RR=\RR$. Dimensionally reducing the family $Q_t$ along $L\times N\rightarrow L\times N_\RR$ we obtain a family of supercharges which are topological for $t\neq 0$ and has 4 invariant directions for $t=0$. In other words, at $t=0$ we get the minimal twist and at $t\neq 0$ the topological twist.

\begin{thm}
The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:7dHodgetwist}
\end{thm}

@@

\subsection{\texorpdfstring{$\cN=(1, 0)$}{N=(1, 0)} Super Yang--Mills}

The general setup for $\cN=(1, 0)$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. Let $U$ be a complex symplectic $\fg$-representation. We consider $\cN=(1, 0)$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. We fix $W_- = 0$ and $W_+=\CC^2$ equipped with a symplectic structure. The $R$-symmetry group depends on the type of the representation $U$:
\begin{itemize}
\item In general, the theory admits an $R$-symmetry group $G_R=\SU(2)$ with $W_+$ the two-dimensional defining representation.

@@

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 0)$ super Yang--Mills on $M=\RR^6$ with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong \CC^3$ with the space of fields $\map(M, U\ham \fg)$. Moreover, the equivalence is $\MU(3)$-equivariant.
\label{thm:6dholomorphictwist}
\end{thm}
\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}. First, we eliminate the fields $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}.  We then observe that the action includes the terms $\int \dvol  (\rho, A_{1,0}^*)$ and $\int \dvol (\wt\nu, \nu^*)$.  In other words, the pairs $(\rho, A_{1,0})$ and $(\nu, \wt\nu)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}. The twisted theory is therefore perturbatively equivalent to the theory with the BV action 
\begin{align*}
 S_{\mr{BV}} &= \int \xi \ol \dd_{A_{0,1}} B  + \psi \wedge \ol \dd_{A_{0,1}} \psi \\
 &+ \dvol\left(\frac 12 (F_{0,2}, B^*) + \frac 12 (\ol \dd_{A_{0,1}} \phi, \psi^*) +  (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([B, c], B^*) + ([\xi, c], \xi^*) + \frac{1}{2}[c, c]c^* +  [\phi, c] \phi^* + ([\psi, c],\psi^*)\right).
\end{align*}
Up to rescaling of the antifields, this is the action functional of the required theory.
%where $A_{0,\bu} = c + A_{0,1} + B + \xi^*$ and $B_{3, \bu} = \xi + B^* + A_{0,1}^*+ c^*$. 
\end{proof}

@@

Let $L=\CC^2$ equipped with a Hermitian structure, $N_\RR=\RR^2$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 8-dimensional spacetime $V^8_\RR=L\times N$ and the 6-dimensional spacetime $V^6_\RR=L\times N_\RR$. Under the projection $V^8_\RR\rightarrow V^6_\RR$ a holomorphic square-zero supercharge $Q$ in 8 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions. Therefore, from Theorem \ref{thm:8dBFreduction} we obtain the following statement.

\begin{thm}
The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$. Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
\end{thm}

@@

Let $L=\CC^2$ equipped with a Hermitian structure and a complex half-density, $N_\RR=\RR^2$ equipped with a Euclidean structure and $N=N_\RR\otimes_\RR\CC$ its complexification. Consider the 8-dimensional spacetime $V^8_\RR=L\times N$ and the 6-dimensional spacetime $V^6_\RR=L\times N_\RR$. Under the projection $V^8_\RR\rightarrow V^6_\RR$ the family $Q_t$ of 8-dimensional square-zero supercharges given by equation \eqref{eq:8dHodgefamily} dimensionally reduces to a family of square-zero supercharges which are topological for $t\neq 0$ and have 4 invariant directions at $t=0$. So, we get a rank $(1, 1)$ partially topological twist at $t=0$ and a rank $(1, 1)$ topological twist at $t\neq 0$. Therefore, from Theorem \ref{thm:8dHodgereduction} we obtain the following statement.

\begin{thm}
The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^2\times \RR^2_{\mathrm{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(2)\times \Spin(2, \RR)$-equivariant.
\label{thm:6dHodgetwist}
\end{thm}

@@

We consider $L=\CC$ equipped with a Hermitian structure and a complex half-density. From Theorem \ref{thm:10dCSreduction} we obtain the following statement.

\begin{thm}
The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
\label{thm:6drank22}
\end{thm}

\section{Dimension 5}

The 5-dimensional supersymmetry algebra has odd part $\Sigma\cong S\otimes W$, where $S$ is the 4-dimensional spin representation of $\Spin(5, \CC)\cong \Sp(4, \CC)$ and $W$ is a complex symplectic vector space. The spin representation carries a symplectic paring $S\otimes S\rightarrow \CC$.

There are Yang--Mills theories with $\cN=1$ or $\cN=2$ supersymmetry, which we consider separately.

\subsection{\texorpdfstring{$\mc N = 1$}{N=1} Super Yang--Mills}
\label{5d_1_section}

We fix $W = \CC^2$ equipped with a symplectic structure. Let $U$ be a symplectic $\fg$-representation. The 5d $\cN=1$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory.

The $R$-symmetry group coincides with the $R$-symmetry group in 6 dimensions:
\begin{itemize}
\item For a general $U$ the $R$-symmetry group is $G_R=\SU(2)$ with $W$ the two-dimensional defining representation.

\item For $U=T^* R$ the $R$-symmetry group is $G_R=\SU(2)\times \U(1)$, where $\U(1)$ acts trivially on $W$, with weight $1$ on $R$ and with weight $-1$ on $R^*$.
\end{itemize}

The theory admits a unique twist:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 3 invariant directions. There is a twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)\hookrightarrow \SU(2)$, so the twisted theory carries an $\MU(2)$-action.
\end{itemize}

A square-zero supercharge $Q$ has rank 1, i.e. $Q=q_+\otimes w_1$ for some $w_1\in W$. We also choose $w_2\in W$ such that $(w_1, w_2) = 1$. We have a twisting homomorphism
\[\phi\colon\MU(2)\xrightarrow{\det^{1/2}}\U(1)\subset \SU(2)\]
such that $W\cong \det(L)^{-1/2} w_1\oplus \det(L)^{1/2} w_2$.

As in Section \ref{sect:9dminimaltwist}, the data of $q_+$ is equivalent to the choice of a one-dimensional subspace $N_\RR\subset V_\RR$ and a complex structure on $V_\RR/N_\RR$ together with a complex half-density.

We will perform a computation of the twist in a more general setting which will be useful for lower-dimensional computations.

Suppose $L$ is a complex vector space equipped with a Hermitian structure. Suppose $N_\RR=\RR^{3-\dim(L)}$ equipped with a Euclidean metric and a spin structure. Denote by $N=N_\RR\otimes_\RR\CC$ its complexification which carries a complex half-density. Let $V_\RR=L\times N$ (a 6-dimensional real vector space). We set $W^6_+=\det(L)^{-1/2}w_1\oplus \det(L)^{1/2} w_2$ as a representation of $\MU(L)$. By the results of Section \ref{sec:6dholomorphictwist}, there is a canonical square-zero supercharge $Q=q_+\otimes w_1\in\Sigma$ determined by the complex structure on $L\times N$ and a complex half-density on $N$.

The dimensional reduction of 6d super Yang--Mills on $L\times N$ alond $\Re\colon N\rightarrow N_\RR$ is by definition the $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges. Since $N\cong N_\RR\oplus iN_\RR$, this theory carries an action of the $R$-symmetry group $G_R=\SU2W)\times \Spin(N_\RR)$. We consider a twisting homomorphism
\[\phi\colon \MU(L)\times \Spin(N_\RR)\rightarrow G_R=\SU(2)\times \Spin(N_\RR)\]
whose first component is $\MU(L)\rightarrow \SU(2)$ as before and the second component is the identity.

\begin{thm}
The twist by $Q$ of $(3+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ with 8 supercharges and matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, U\ham \fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:6dCSreduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:6dholomorphictwist} the twist of 6d $\cN=(1, 0)$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $\map(L\times N, U\ham \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $\map(L\times N_\RR, U\ham\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}
